---
title: "Iteration"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(ggplot2)

options(scipen = 999)

knitr::opts_chunk$set(
        collapse = TRUE, 
        message = FALSE, 
        warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
  )

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1

```{r}
set.seed(123)

# function
sim_birthday = function(n){
  birthdays = sample(1:365, n, replace = TRUE)
  
  return(length(unique(birthdays)) < n)
}

# 10000 times
sim_birthday_df = 
  expand.grid(
    sample_size = 2:50,
    iter = 1:10000
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_birthday)
  ) |> 
  unnest(estimate_df)

prob_df = 
  sim_birthday_df |> 
  group_by(sample_size) |> 
  summarize(
    prob = mean(estimate_df)
  )

# plot
ggplot(prob_df, aes(x = sample_size, y = prob)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Probabilty of sharing a Birthday and Group Size",
    x = "Group size",
    y = "Probability"
  )
```

There is a positive association between the probability that at least two people in the group will share a birthday and the group size.

### Problem 2

```{r}
set.seed(123)

# calculate power
my_power = function(mu_0, n = 30, sigma = 5) {
  x = rnorm(n, mean = mu_0, sd = sigma)

  t_result = t.test(x, mu = 0) |> broom::tidy()
  
  tibble(
    estimate = t_result$estimate,
    p_value = t_result$p.value
  )
}

# for mu list
sim_powers_df = function(mu_list, iteration = 5000){
  expand_grid(
    mu = mu_list,
    iter = 1:iteration
  ) |> 
  mutate(
    estimate_df = map(mu, my_power)
  ) |> 
  unnest(estimate_df)
}

# result
mu_list = 0:6
sim_results_df = sim_powers_df(mu_list)

sim_results_plot = sim_results_df |> 
  mutate(
    rej = ifelse(p_value < .05, 1, 0)
  )
```

```{r}
sim_results_plot1 = sim_results_plot |> 
  group_by(mu) |> 
  summarize(
    rej_rate = mean(rej),
    avg_estimate = mean(estimate),
    avg_estimate_rej = mean(estimate[rej == 1])
  ) |> 
  filter(mu != 0)

# plot 1
plot1 = 
  ggplot(sim_results_plot1, aes(x = mu, y = rej_rate)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    title = "Association Between Power of the T-Test And Effect Size",
    x = "True value of μ",
    y = "Proportion of rejections (Power)"
  )

plot1
```

Plot 1 suggests that the proportion of times the null was rejected increases with increasing effect size. They are positive associated and the power is equal to 1 after $ \mu = 5$.

```{r}
# plot 2
plot2 = 
  ggplot(sim_results_plot1, aes(x = mu)) +
  geom_line(aes(y = avg_estimate, color = "Estimate Overall"), size = 1) +
  geom_point(aes(y = avg_estimate, color = "Estimate Overall")) +
  geom_line(aes(y = avg_estimate_rej, color = "Estimate for Rejected Tests"), size = 1) +
  geom_point(aes(y = avg_estimate_rej, color = "Estimate for Rejected Tests")) +
  scale_color_manual(
    values = c("Estimate Overall" = "blue", "Estimate for Rejected Tests" = "red")
  ) +
  labs(
    title = "Average Estimate of μ overall and for Tests with Rejection Only",
    x = "True value of μ",
    y = "Average Estimate of μ"
  ) +
  theme(legend.title = element_blank())

plot2
```

Plot 2 suggests that the sample average of $ \hat{\mu} $ across tests with rejection and the true value of $ \mu $ are not equal, because the sample mean is significantly different from 0 in the null hypothesis, and then the p-value < .05.

```{r}
write.csv(sim_results_plot, "data/p2_sim_results.csv", row.names = FALSE)
ggsave("data/plot1.png", plot = plot1)
ggsave("data/plot2.png", plot = plot2)
```


### Problem 3

```{r}
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/refs/heads/master/homicide-data.csv"
raw_dat = read_csv(url, na = c("Unknown", ""))

skimr::skim(raw_dat)
```

There are `r nrow(raw_dat)` observations and `r ncol(raw_dat)` variables in the dataset, including 8 character variables (e.g., city, state, disposition) and 4 numeric variables (e.g., victim_age, lat). 

```{r}
dat = raw_dat |> 
  janitor::clean_names() |> 
  mutate(
    city_state = paste(city, state, sep = ", ")
  )

summary = dat |> 
  group_by(city_state) |> 
  summarize(
    homicides = n(),
    homicides_unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"), na.rm = TRUE)
  )

summary
```

```{r}
# Baltimore, MD
baltimore_summary = summary |> 
  filter(city_state == "Baltimore, MD")

baltimore_test =
  prop.test(
  x = baltimore_summary |> pull(homicides_unsolved),
  n = baltimore_summary |> pull(homicides)
)

baltimore_results = broom::tidy(baltimore_test)
baltimore_estimates = baltimore_results |> 
  select(estimate, conf.low, conf.high)

baltimore_estimates
```

```{r}
# Each city
summary_nest = nest(summary, data = homicides:homicides_unsolved)

my_prop_test = function(df) {
  test_result = prop.test(x = df$homicides_unsolved, n = df$homicides)
  test_result = test_result |> 
    broom::tidy() |> 
    select(estimate, conf.low, conf.high)
} 

city_summary = summary_nest |> 
  mutate(
    results = map(data, my_prop_test)
  ) |> 
  unnest()

city_summary
```

```{r}
plot3 = 
  ggplot(city_summary, aes(x = fct_reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Proportion"
  ) +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1)
  )

plot3
```

```{r}
write.csv(summary, "data/homicide_summary.csv", row.names = FALSE)
ggsave("data/plot3.png", plot = plot3)
```

